\documentclass[a4paper,11pt]{article}
\usepackage[left=0.6in, right=0.6in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, left=0pt}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{url}
\urlstyle{same}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.1}

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{8pt}{6pt}
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\begin{document}
\small
\begin{center}
    {\huge \textbf{DEEPAK MODI}} \\
    \vspace{6pt}
    Gurugram, IN~\textbar~+91 8676842176~\textbar~\href{mailto:deepakmodidev@gmail.com}{\nolinkurl{deepakmodidev@gmail.com}}~\textbar~\href{https://deepakmodi.tech}{\texttt{deepakmodi.tech}}
\end{center}

\section*{SUMMARY}
Final-year B.Tech CSE student and aspiring software engineer with experience building full-stack applications used by 1000+ users. Solved 300+ DSA problems and delivered real-world projects through internships and freelance work. Skilled in React, Node.js, and TypeScript, with a strong passion for building performant, user-centric software.

\section*{TECHNICAL SKILLS}
\textbf{Programming Languages:} Java, JavaScript, TypeScript, Python, C++ \\
\textbf{Web Development:} React.js, Next.js, Node.js, Express.js, REST APIs, Tailwind CSS \\
\textbf{Databases:} MongoDB, MySQL, PostgreSQL, Firebase (Cloud Firestore) \\
\textbf{Tools \& Platforms:} Git, GitHub, VS Code, Firebase Auth, Gemini API, Postman, Linux/Unix CLI \\
\textbf{CS Fundamentals:} OS, Computer Networks (CN), DBMS, OOPs, Software Engineering \\
\textbf{Basic Skills:} System Design (basics), AWS (basics), DevOps & CI/CD (basics)

\section*{EXPERIENCE}
\textbf{CyberXield} \hfill \textit{Jan 2024 -- Feb 2024} \\
\textit{Front-End Web Developer Intern}
\begin{itemize}
    \item Built responsive and cross-browser compatible company websites using HTML, CSS, and JavaScript.
    \item Enhanced front-end UI/UX by redesigning visual components, leading to a 20\% boost in user interaction metrics.
    \item Collaborated closely with design, QA, and product teams to deliver polished and production-ready features.
\end{itemize}

\section*{PROJECTS}

\textbf{ResumeGPT} \hfill \href{https://tryresumegpt.vercel.app}{\texttt{tryresumegpt.vercel.app}}
\begin{itemize}
    \item Developed an AI-powered resume builder that generates professional resumes from natural language prompts.
    \item Implemented with Next.js, TypeScript, Prisma, NextAuth, and Google Gemini API for seamless user experience.
    \item Attracted 100+ users within the first month and received good feedback for ease of use and multiple templates.
\end{itemize}

\vspace{6pt}

\textbf{NotesNeo} \hfill \href{https://notesneo.vercel.app}{\texttt{notesneo.vercel.app}}
\begin{itemize}
    \item Developed an online study notes platform used by 1000+ university students for semester-wise notes access.
    \item Engineered personalized user dashboards with secure login, favorites, and mobile-friendly UI.
    \item Built using React, TypeScript, Firebase Auth, Firestore, Tailwind CSS, deployed via Vercel.
\end{itemize}

\vspace{6pt}

\textbf{NeoCompiler} \hfill \href{https://necompiler.vercel.app}{\texttt{necompiler.vercel.app}}
\begin{itemize}
    \item Created a real-time multi-language code editor with 10+ language support, public sharing, and snippet saving.
    \item Integrated Monaco Editor, Gemini API for AI help, and Piston API for seamless backend code execution.
    \item Enabled social coding with user profile, theming, and community feed using React, Google OAuth, Node.js.
\end{itemize}

\vspace{6pt}

\textbf{Braineo} \hfill \href{https://braineo.vercel.app}{\texttt{braineo.vercel.app}}
\begin{itemize}
    \item Built an AI-powered learning platform with flashcards, quizzes, and career-focused learning path experiences.
    \item Delivered personalized experiences via Gemini Flash 2.0 \& Llama 3.0 based on goals, skills, and assessment.
    \item Designed, engineered, and responsive UI with React, Next.js, Prisma, Planetscale, and Gemini SDK.
\end{itemize}

\section*{EDUCATION}
\textbf{St. Andrews Institute of Technology and Management (MDU Rohtak)} \hfill \textit{2022 -- 2026} \\
\textit{Bachelor of Technology, Computer Science Engineering} \hfill \textbf{Percentage:} 76\% \\
\textbf{Inter Science College, Hazaribagh} \hfill \textit{2019 -- 2021} \\
\textit{Senior Secondary, PCM with Computer Science} \hfill \textbf{Percentage:} 88\% \\
\textbf{St. Pauls School, Hazaribagh} \hfill \textit{2019} \\
\textit{Secondary Education} \hfill \textbf{Percentage:} 85.6\%

\section*{ACHIEVEMENTS}
\textbf{Innoviz 2023 -- First Prize Winner, Tech Exhibition} \\
Led a 4-member team to develop an ``Anti-Sleep Accident Preventer'' to detect driver drowsiness using sensors. Designed a hardware prototype using eye-tracking sensors, buzzers, and alert systems for driver safety. Secured 1st position among 100+ teams judged on innovation, practicality, and technical execution impact.

\end{document}