\documentclass[a4paper,11pt]{article}
\usepackage[left=0.6in, right=0.6in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, left=0pt}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{url}
\urlstyle{same}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.1}

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{8pt}{6pt}
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\begin{document}
\small
\begin{center}
    {\huge \textbf{DEEPAK MODI}} \\
    \vspace{6pt}
    New Delhi, IN~\textbar~+91 8676842176~\textbar~\href{mailto:deepakmodi8676@gmail.com}{\nolinkurl{deepakmodi8676@gmail.com}}~\textbar~\href{https://deepakmodi.tech}{\texttt{deepakmodi.tech}}
\end{center}

\section*{SUMMARY}
Full-Stack Developer and final-year B.Tech CSE student with expertise in AI web integrations, currently working at a Y Combinator-backed startup. Proven track record building scalable applications serving 1000+ users with experience in React, Next.js, TypeScript, and modern web technologies. Solved 300+ DSA problems and delivered production-ready solutions through internships and freelance projects.

\section*{TECHNICAL SKILLS}
\textbf{Programming Languages:} JavaScript (ES6+), TypeScript, Java, Python, C++ \\
\textbf{Web Development:} HTML5, CSS3, React.js, Next.js, Node.js, Express.js, REST APIs, GraphQL, Tailwind CSS \\
\textbf{Databases:} MongoDB, MySQL, PostgreSQL, Firebase (Firestore), Supabase \\
\textbf{Tools \& Platforms:} Git, GitHub, VS Code, NPM, Postman, Vercel, Netlify, Docker, AWS, Linux/Unix CLI \\
\textbf{Generative AI \& Automation:} LLMs, NLP, RAG, LangChain, AI Agents, Vector Databases, Gemini API \\
\textbf{Other Skills:} System Design, CI/CD (GitHub Actions), Unit Testing, Data Visualization, Prisma ORM

\section*{EXPERIENCE}
\textbf{Frontend Developer Intern} \hfill \textit{September 2025 -- Present} \\
\textit{Cekura AI (YC F24), San Francisco, CA (Remote)} \hfill \href{https://www.cekura.ai}{\texttt{cekura.ai}}
\begin{itemize}
    \item Working at a Y Combinator-backed startup building the reliability layer for Conversational AI agents.
    \item Contributing to automated testing and monitoring platform for Voice and Chat AI agents serving 75+ customers.
    \item Building intuitive dashboards and user interfaces for AI-powered testing tools, evaluation metrics, and observability features using React, TypeScript, Next.js, Tailwind CSS and shadcn UI.
\end{itemize}

\vspace{4pt}

\textbf{Software Development Intern} \hfill \textit{July 2025 -- September 2025} \\
\textit{Nile Wellness \& Medicare Pvt Ltd, Gurugram, Haryana (Remote)} \hfill \href{https://www.nilewellness.com}{\texttt{nilewellness.com}}
\begin{itemize}
    \item Built treatment landing pages and multi-tenant lead generation website for 5 major Indian hospitals (Apollo, Fortis, Artemis, Max Healthcare, Medanta) serving international patients.
    \item Converted 50+ Figma designs into React components with responsive, mobile-friendly layouts.
    \item Integrated OneSignal push notifications, Google Ads tracking, Tawk.to live chat, and Google Translate for multi-language support using React, Next.js, TypeScript, Tailwind CSS, and Radix UI.
\end{itemize}

\section*{PROJECTS}

\textbf{ResumeGPT} \hfill \href{https://tryresumegpt.vercel.app}{\texttt{tryresumegpt.vercel.app}}
\begin{itemize}
    \item Developed an AI-powered resume builder that generates professional resumes from natural language prompts.
    \item Scaled to 200+ active users with ATS compatibility analysis and real-time scoring using RAG and NLP techniques.
    \item Implemented with Next.js, TypeScript, Prisma, NextAuth, and Google Gemini API for seamless user experience.
\end{itemize}

\vspace{6pt}

\textbf{NotesNeo} \hfill \href{https://notesneo.vercel.app}{\texttt{notesneo.vercel.app}}
\begin{itemize}
    \item Developed an online study notes platform used by 1000+ university students for semester-wise notes access.
    \item Engineered personalized user dashboards with secure login, favorite system, and mobile-friendly responsive UI.
    \item Built using React, TypeScript, Firebase Auth, Firestore, Tailwind CSS with optimized performance and SEO.
\end{itemize}

\vspace{6pt}

\textbf{NeoCompiler} \hfill \href{https://neocompiler.vercel.app}{\texttt{neocompiler.vercel.app}}
\begin{itemize}
    \item Created a real-time multi-language code editor with 10+ language support, public sharing, and snippet saving.
    \item Integrated Monaco Editor, Gemini API for AI help, and Piston API for seamless backend code execution.
    \item Enabled social coding with user profiles, theming, and community feed using React, Google OAuth, and Node.js.
\end{itemize}

\vspace{6pt}

\textbf{Braineo} \hfill \href{https://braineo.vercel.app}{\texttt{braineo.vercel.app}}
\begin{itemize}
    \item Built an AI-powered learning platform with flashcards, quizzes, and career-focused learning path generation.
    \item Delivered personalized experiences via Gemini Flash 2.0 \& Llama 3.3 based on age, goals, and skill assessment.
    \item Designed a modern, animated, and responsive UI with React, Appwrite backend, Framer Motion, and Vercel.
\end{itemize}

\section*{EDUCATION}
\textbf{Maharshi Dayanand University, Rohtak} \hfill \textit{2022 -- 2026} \\
\textit{Bachelor of Technology, Computer Science Engineering} \hfill \textbf{Percentage:} 80\% \\

\end{document}
